Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
sec2.2
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\section{Introduction}
\label{introduction}

@@

Allowing users to define custom code that executes in the storage nodes is a 
useful technique for offloading computation closer to where the data is stored 
in order to significantly reduce the amount of data moved between storage 
servers and clients.
Ceph provides object storage via 
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. 
Ceph provides a rich plugin framework for defining new interfaces to objects
stored within RADOS, effectively allowing developers to use co-design
techniques to define logical storage devices tailored to their application
domain.

An object interface plugin is structured in a similar way to that of an RPC in
which a developer creates a named function within the cluster that clients may
invoke upon an object. In Ceph these functions are defined by a composition of
existing native interfaces that include reading and writing bytestream data
and controlling snapshots and cloning, all of which may be transactionally
composed with full access to a sorted key-value service allowing applications
to fine tune storage interfaces, such as using a read-modify-write guard to
protect shared data.

\paragraph*{Malacology:}  The implementation of Ceph's object abstraction, although powerful, has some 
drawbacks.
Supporting only C/C++ for object interface developers, Ceph requires
distribution of compiled binaries for the correct architecture, adding a
large barrier of entry for developers and system administrators. Second,
having no way to dynamically unload modules, any changes require a full
restart of an OSD which may have serious performance impacts due to a loss
of cached data. And finally, the security limitations of the framework
limit the use of object classes to all but those with administrative level
access and technique expertise.

By embedding the Lua runtime, Malacology makes the base RADOS API available in a 
dynamic environment, resulting in a object storage API with economy of 
expression, which at the same time provides the full set of features of the base 
object class. New object interfaces that are expressed in thousands of lines of 
code can be implemented in approximately an order of magnitude less 
code~\cite{geambasu_comet_2010}.

@@

\subsection{Metadata Load Balancing}
\label{malacology:mds}

>>>>

\section{Introduction}
\label{introduction}
\label{sec:intro}

@@

@@

Briefly described in Section~\section{sec:intro}, Ceph supports the creation
of application-specific object interfaces~\cite{weil_rados_2007}. The ability
to offload computation can reduce data movement, and transactional interfaces can
significantly simplify construction of complex storage interfaces that require
uncoordinated parallel access.

An object interface is a plugin structured in a similar way to that of an RPC
in which a developer creates a named function within the cluster that clients
may invoke. In the case of Ceph each function is implicitly run within the
context of an object specified when the function is invoked. Developers of
object interfaces express behavior by creating a composition of native
interfaces or other custom object interfaces, and handle serialization of
function input and output. A wide range of native interfaces are available to
developers, such as reading and writing to a bytestream, controlling snapshots
and clones, all of which may be transactionally composed with access to a
sorted key-value service allowing applications to create rich interfaces, such
as using a read-modify-write guard to protect a shared index defined over
content store in a byte stream.

\paragraph*{Malacology:} The implementation of Ceph's object abstraction,
although powerful, has some drawbacks. Supporting only C/C++ for object
interface developers, Ceph requires distribution of compiled binaries for the
correct architecture, adding a large barrier of entry for developers and
system administrators. Second, having no way to dynamically unload modules,
any changes require a full restart of an OSD which may have serious
performance impacts due to a loss of cached data~\cite{facebook-mysql}. And
finally, the security limitations of the framework limit the use of object
classes to all but those with administrative level access and deep technical
expertise.

To address these concerns, Malacology takes advantage of community contributed
Lua extensions to Ceph allowing new object interfaces to be dynamically loaded
into the system and modified at runtime, resulting in a object storage API
with economy of expression, which at the same time provides the full set of
features of the base object class~\cite{bdmc}. New object interfaces that are
expressed in thousands of lines of code can be implemented in approximately an
order of magnitude less code~\cite{geambasu_comet_2010}.

All of these modifications work in tandem to implement the desired behavior,
and are typically co-designed together such that each depends on the other to
behave as expected. In highly dynamic environments such as a distributed
storage system, changes to the system propagate at variable rates, requiring
all components of the system to be able to adapt. Thus, system services
realized through extensibility should be versioned together as a group,
exposing the version to allow introspection and domain-specific treatment of
version mismatch scenarios.

And finally, it is important to not underestimate the importance of the
preservation of the modifications that enable a new system service. In many
(if not all) cases, interfaces defining access to data are just as important
as the data itself by virtue of inherently providing structural context. Thus,
all components of a system service must be kept to the same standards of
protection as data in the system itself.

To this end we have extended the monitoring service using the framework
described in Section~\ref{sec:mon} to provide an interface for registration
and verification of dynamically defined object interfaces. Using this service
guarantees that interface definitions are not only made durable, but are
transparently and consistently propogated throughput the cluster and that
clients are properly synchronousized with the latest interfaces.

\subsection{Distributed Metadata Services}
\label{malacology:mds}
